### 2014-05-04 docs/seminar/conclusion.tex
revising
changed some small stuff in other places, but mostly in conclusion

\section{Conclusion and Future Work}
\label{sec:conclusion}
In the paper, we put forward a comprehensive solution for implementation and design of a translator-expert retrieval system. As well as system architecture, we thoroughly study the obstacles and pitfalls in implementation of such a system. Document aggregation as well as ranking problems are two main issues thoroughly discussed in the paper and followed by provided solutions.

The first issue concerns with the comparison of the aggregation methods. The aggregation methods estimate the proficiency of each translator based on the similarity values of the previous translated documents with the query document. Using the assessment of the proof-readers on the final translation as the golden data, we compare three aggregation methods. Finally, GP2 method shows better performance in comparison to the others with reasonable good results.

The second issue tackles the problem of experts ranking. By applying different learning to rank algorithms, we obtain a ranking model based on linear regression with fairly good performance. The model's performance is approved by both NDCG and ERR evaluation measures. Feature analysis of data indicates the importance of price and delivery time in comparison to the other features for the the human annotators.

Recently, different aspects of expert retrieval platforms drawing an increasing interest. Based on the current study, we aim to accomplish a comprehensive aggregation method regarding to the translation context in the following studies.

>>>>

%\vspace{-0.2cm}
\section{Conclusion and Future Work}
%\vspace{-0.2cm}
\label{sec:conclusion}
We propose a comprehensive solution for a translator-expert retrieval system. As well as system architecture, we thoroughly study the obstacles and pitfalls in implementing such a system. Multilingual IR tools are adapted to solve two essential steps in a practical system: Estimating the translators proficiency on a particular topic (document aggregation), ranking translators based on real-world factors (learning to rank).  %as well as ranking problems are two main issues thoroughly discussed in the paper and followed by provided solutions.

To address the first issue we have compared three commonly used aggregation methods. The aggregation methods estimate the proficiency of each translator based on the similarity values of the previous translated documents with the query document. Using the assessment of the proof-readers on the final translation as the golden data, we compare three aggregation methods. We found that the GP2 method shows better performance in comparison to the others with reasonable good results. Future work in addressing the estimation of translators' proficiency will allow us to increase the correlation between the aggregation and proof-readers' scores.

The second issue tackles the problem of experts ranking. By applying different learning to rank algorithms, we obtain a ranking model based on linear regression with a very high performance. The model's performance is tested with both NDCG and ERR evaluation measures. Feature analysis of data shows that real users consider  price and delivery time much more important than the other features. This is relatively disappointing, but in retrospective not surprising for a real-world system.

%Recently, different aspects of expert retrieval platforms drawing an increasing interest. Based on the current study, we aim to accomplish a comprehensive aggregation method regarding to the translation context in the following studies.

### 2014-05-04 docs/seminar/evaluation.tex
changed some small stuff in other places, but mostly in conclusion

\begin{figure}
\centering
\begin{subfigure}{.3\textwidth}
  \centering
	\includegraphics[width=0.99\textwidth]{figures/aggregation_plots_gp2.png}
	\caption{GP2}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
	\includegraphics[width=0.99\textwidth]{figures/aggregation_plots_top5.png}
	\caption{TOP5}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
	\includegraphics[width=0.99\textwidth]{figures/aggregation_plots_top1.png}
	\caption{TOP1}
\end{subfigure}
\vspace{-0.3cm}
\caption{Data distribution of aggregation values against proof-readers' assessments. Axes X shows the assessments of proof-readers. axes Y represents the values of the corresponding aggregation function}
\label{fig:aggregationplot}
\vspace{-0.3cm}
\end{figure}

@@

\begin{table}
\vspace{-0.3cm}
\centering
\begin{tabular}{c c|c|c|c|}
\cline{3-5} & & Top1 & Top5 & GP2  \\
\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$r_s$}} & Correlation Test & 0.052 & 0.089 & 0.145\\
\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.4866 & 0.2295 & 0.05038\\
\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$\tau$}} & Correlation Test & 0.034 & 0.059 & 0.102\\
\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.5157 & 0.2562 & 0.05263\\
\hline
\end{tabular}
\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks as well as P-Value of Significance of Correlation Test}
\label{table:correlation}
\end{table}

\subsection{Learning To Rank}
In order to accumulate data required for ranking model, we conduct a survey with eight human annotators. The questions of survey represent three translators each with four criteria (price, delivery time, proficiency and number of cooperation times). As mentioned before, in order to prevent bias in results, the name and the picture of the translators are hidden from the annotators. The annotators rate the questions from one to three based on \textit{Total Order} strategy. The accumulated data consists of $400$ annotated list and overall $1200$ records.

@@

\begin{table}
\vspace{-0.3cm}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline \multirow{2}{*}{Method} & \multicolumn{2}{ c| }{NDCG@3} & \multicolumn{2}{ c| }{ERR@3}  \\
\cline{2-5} & Result & Random & Result & Random \\
\hline Linear Regression & \textbf{0.935} & 0.833 & \textbf{0.451} & 0.375 \\
\hline RankNet & 0.876 & 0.834 & 0.394 & 0.378 \\
\hline RankBoost & 0.909 & 0.831 & 0.432 & 0.374 \\
\hline LambdaMART & 0.93 & 0.832 & 0.447 & 0.373 \\
\hline ListNet & 0.915 & 0.831 & 0.439 & 0.375 \\
\hline AdaRank & 0.857 & 0.83 & 0.399 & 0.373 \\
\hline Random Ranker & 0.832 & 0.832 & 0.375 & 0.378 \\
\hline
\end{tabular}
\caption{Results of applying Learning to Rank methods based on NDCG and ERR evaluation measures}
\label{table:l2rresult}
\end{table}

\begin{figure}
\centering
\includegraphics[scale=0.6]{figures/l2rdiagram.png}
\caption{Learning to Rank Results}
\label{fig:l2rdiagram}
\end{figure}

\begin{table}
\vspace{-0.3cm}
\centering
\begin{tabular}{|c|c|}
\hline Feature & Value  \\
\hline Price & 2.002 \\
\hline Duration & 0.057 \\
\hline Proficiency & -0.048 \\
\hline Number of Cooperation Times & -0.313 \\
\hline
\end{tabular}
\caption{Coefficient value of features in Linear Regression model}
\label{table:l2rcoefficient}
\end{table}

>>>>

\begin{figure}
\centering
\begin{subfigure}{.3\textwidth}
  \centering
	\includegraphics[width=0.99\textwidth]{figures/aggregation_plots_gp2.png}
	\caption{GP2}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
	\includegraphics[width=0.99\textwidth]{figures/aggregation_plots_top5.png}
	\caption{TOP5}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
	\includegraphics[width=0.99\textwidth]{figures/aggregation_plots_top1.png}
	\caption{TOP1}
\end{subfigure}
\vspace{-0.3cm}
\caption{Data distribution of aggregation values against proof-readers' assessments. The x-axis shows the assessments of proof-readers, while the y-axis represents the values of the corresponding aggregation function}
\label{fig:aggregationplot}
\vspace{-0.3cm}
\end{figure}

@@

\begin{table}
\vspace{-0.3cm}
\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks as well as P-Value of Significance of Correlation Test}
\centering
\begin{tabular}{c c|c|c|c|}
\cline{3-5} & & Top1 & Top5 & GP2  \\
\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$r_s$}} & Correlation Test & 0.052 & 0.089 & 0.145\\
\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.4866 & 0.2295 & 0.05038\\
\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$\tau$}} & Correlation Test & 0.034 & 0.059 & 0.102\\
\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.5157 & 0.2562 & 0.05263\\
\hline
\end{tabular}
\label{table:correlation}
\vspace{-0.3cm}
\end{table}

\subsection{Learning To Rank}
\vspace{-0.2cm}
In order to accumulate data required for ranking model, we conduct a survey with eight human annotators. The questions of survey represent three translators each with four criteria (price, delivery time, proficiency and number of cooperation times). As mentioned before, in order to prevent bias in results, the name and the picture of the translators are hidden from the annotators. The annotators rate the questions from one to three based on \textit{Total Order} strategy. The accumulated data consists of $400$ annotated list and overall $1200$ records.

@@

\begin{table}
\vspace{-0.3cm}
\caption{Results of applying Learning to Rank methods based on NDCG and ERR evaluation measures}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline \multirow{2}{*}{Method} & \multicolumn{2}{ c| }{NDCG@3} & \multicolumn{2}{ c| }{ERR@3}  \\
\cline{2-5} & Result & Random & Result & Random \\
\hline Linear Regression & \textbf{0.935} & 0.833 & \textbf{0.451} & 0.375 \\
\hline RankNet & 0.876 & 0.834 & 0.394 & 0.378 \\
\hline RankBoost & 0.909 & 0.831 & 0.432 & 0.374 \\
\hline LambdaMART & 0.93 & 0.832 & 0.447 & 0.373 \\
\hline ListNet & 0.915 & 0.831 & 0.439 & 0.375 \\
\hline AdaRank & 0.857 & 0.83 & 0.399 & 0.373 \\
\hline Random Ranker & 0.832 & 0.832 & 0.375 & 0.378 \\
\hline
\end{tabular}
\vspace{-0.3cm}
\label{table:l2rresult}
\end{table}

\begin{figure}
\centering
\includegraphics[scale=0.6]{figures/l2rdiagram.png}
\vspace{-0.3cm}
\caption{Learning to Rank Results}
\label{fig:l2rdiagram}
\end{figure}

\begin{table}
\vspace{-0.3cm}
\caption{Coefficient value of features in Linear Regression model}
\centering
\begin{tabular}{|c|c|}
\hline Feature & Value  \\
\hline Price & 2.002 \\
\hline Duration & 0.057 \\
\hline Proficiency & -0.048 \\
\hline Number of Cooperation Times & -0.313 \\
\hline
\end{tabular}
\label{table:l2rcoefficient}
\end{table}
